Cell Decompositions for Rank Two Quiver Grassmannians

### 2019-06-21 Grassmannian_cells.tex
Lemma 3.15

\begin{lemma}
  \label{le:projective subrepresentations}
  For $V\in \Gr(\cH_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
\end{lemma}
\begin{proof}
  We proceed by induction on $m$.
  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.

  For $m\ge2$, we observe by induction that Lemma~\ref{le:reflected truncated preprojectives} implies any subrepresentation of $P_{m+1}^V$ which has no summand isomorphic to $P_1$ must be a direct sum of preprojective representations $P_r$ with $2\le r\le m$.
  Indeed, each of these is obtained from a subrepresentation of $\Sigma_1(P_{m+1}^V)^\sigma$ by applying the functor $\Sigma_2(-)^\sigma$ and the claim follows from the recursions in Remark~\ref{rem:reflection recursion} for preprojective representations.
\qed\end{proof}
% We proceed by induction on $m$.
% When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
% In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.

% For $m\ge2$, we observe by induction that Lemma~\ref{le:reflected truncated preprojectives} implies that any subrepresentation of $P_{m+1}^V$ which has no summand isomorphic to $P_1$ must be a direct sum of preprojective representations $P_r$ with $2\le r\le m$.
% Indeed, each of these is obtained from a subrepresentation of $\Sigma_1(P_{m+1}^V)^\sigma$ by applying the functor $\Sigma_2(-)^\sigma$ and the claim follows from the recursions in Remark~\ref{rem:reflection recursion} for preprojective representations.
%\qed\end{proof}

>>>>

\begin{lemma}
  \label{le:projective subrepresentations}
  For $V\in \Gr(\cH_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
\end{lemma}
\begin{proof}
  Since the map $ev_V$ in equation \eqref{eq:truncated preprojectives} is irreducible, every proper subrepresentation of $P_{m+1}^V$ factors through $P_{m+1}$ and the claim follows from Lemma~\ref{le:preprojective subs}.
  %We proceed by induction on $m$.
  %When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
  %In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.

  %For $m\ge2$, we observe by induction that Lemma~\ref{le:reflected truncated preprojectives} implies any subrepresentation of $P_{m+1}^V$ which has no summand isomorphic to $P_1$ must be a direct sum of preprojective representations $P_r$ with $2\le r\le m$.
  %Indeed, each of these is obtained from a subrepresentation of $\Sigma_1(P_{m+1}^V)^\sigma$ by applying the functor $\Sigma_2(-)^\sigma$ and the claim follows from the recursions in Remark~\ref{rem:reflection recursion} for preprojective representations.
\qed\end{proof}
